### 2017-04-01 manuscript.rmd
dup_adjust reduced from 5 to 2
added trees to repo

	# Name of the compara gene trees file. This is from 
	# ftp://ftp.ensembl.org/pub/release-75/emf/ensembl-compara/homologies/
	# but not included here due to its size. Put it in the kmrr/ directory
	gene_tree_name = "Compara.75.protein.nhx.emf"

@@

	# In simulation, the fold change in rate following duplication relative to speciation
	dup_adjust = 5

>>>>

	# Name of the compara gene trees file. This was downloaded from 
	# ftp://ftp.ensembl.org/pub/release-75/emf/ensembl-compara/homologies/
	# and compressed with gz

	gene_tree_name = "Compara.75.protein.nhx.emf.gz"

@@

	# In simulation, the fold change in rate following duplication relative to speciation
	dup_adjust = 2
